---
title: "Report on Gun Murders"
author: "Logeswaran SR"
date: "2023-11-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Introduction

This is a report on 2010 gun murder rates obtained from FBI Reports. The original Data was obtained from [this Wikipedia Page](https://en.wikipedia.org/wiki/Murder_in_the_United_States_by_state).

To work with it, we have used the library *Tidyverse*, which we have imported in the report already.

The Dataset is already wrangled and saved in a file named: "murders.rda". We load the dataset with the following code

```{r}
load("rda/murders.rda")
```

The summary of the imported dataset is given as:

```{r Summary, echo=FALSE}
summary(murders)
```

## Murder Rate by State

We note the large state to state variability by generating a barplot showing the murder rate by state:

```{r murder-rate-by-state, echo=FALSE}
murders %>% mutate(abb = reorder(abb, rate)) %>%
  ggplot(aes(abb, rate)) +
  geom_bar(width = 0.5, stat = "identity", color = "black") +
  coord_flip()
```
